\section{Introduction}

Welcome to The Scorched Land campaign setting.  The following chapters will lay 
out the most important aspects of this world, however the DM is encouraged to 
alter the setting to fit their groups play style and goals.  Hopefully this document
will be helpful for those first starting to DM and to those that are veterans
alike.  In the following pages, I will attempt to cover all of back-story, party
motivations, possible quests and important NPCs that the party could encounter on 
their adventure.  Due to the size of the map and openness of the storyline, the 
DM will have to fill in many of the blanks.

\section{Background}

A vast ocean encompasses most of the world, and autonomous city-states rule over
what land there is.  The city-state of Antioc, the Empire of Ryujin and the Dwarven
stronghold of Irondale rule most of the world around them.  Few places around the 
world fall outside their spheres of influence, whether it's to do with the 
location or to affiliations with other groups.  

The city-state of Antioc sits on the smallest island in the area, Grindstone Island,
however due to its central location, the city has become rich and powerful.  Antioc
controls most of the trade routes, and serves as a convenient stop for ships 
traveling to other ports.  Archbishop-General Augustus XVII rules over Antioc and 
its colonies, as both the head of the Order of Imodae and the Antiocan military,
Augustus holds supreme rule.  Antioc controls the city of N'Gulonga, which serves 
as a stop for ships bound for the Temple of Imodae to the far north.  The leaders 
of Grindstone Island brokered a deal with the Jade Lady, Empress of Ryjin, allowing
for trade between the two nations.  With this agreement Antioc gained influence 
over trade routes between all the other nations.

The Empire of Ryujin lies to the east of Grindstone Island.  Ryujin maintains a
constant state of isolationism, interacting with the other states only when
necessary.  The walled port of Okashu remains the only city where foreigners may
enter the country, and to travel outside its walls requires express permission 
from the Jade Lady.  As with all things people do not understand, the people
 from the Empire are shrouded in lore and superstition, fighters that can disappear 
into nothingness, warriors that can scare off the most fiendish of beasts and
men that can kill with only a touch.  Very few outsiders are allowed into the 
country and even fewer have seen the Imperial City.  To the north and south of 
Okashu sits Narahashi and Aohiro, respectively.  From these fortressed cities the 
Empire keeps a close watch over all traffic in and out of Okashu.  Ships accused
of smuggling contraband to Okashu are never seen again.  

To the north-west of Grinstone sits Wolf Island, home of the Elvan city of 
Edgehaven. The island has long been coveted for its large old growth forests and 
rich soil.  However the Elvan tribunal know as The Masked Ones and their enforcers
the Order of Gozreh, forbid the taking of natural resources for profit.  Due to
its location and  
