\section{People and Factions}
	
	\subsection{Important NPCs}

		\subsubsection{Augustus XVII}

		\subsubsection{The Masked Ones}

		\subsubsection{Faust}

		\subsubsection{King Faerlag}

		\subsubsection{The Jade Lady}

	\subsection{Minor NPCs}

		\subsubsection{The Man in Red}

		Once a Red Wizard, he has been banished from the Iron Citadel
		for speaking out against the yearly rituals and now lives atop
		a mountain on Haunya.  The local goblin tribe have adopted his
		Iron Band tattoo as their new crest and revere him as a wise 
		and powerful man.  Since the goblins live close to a mountain
		pass used frequently by the Thieves Guild as a smuggling route,
		they now raid carrivans, hoping to catch a group transporting
		some of the relics necessary for the Fires of Dis ritual.  He
		can grant the party information or even a boon depending on how
		he likes or gets a long with them.  A percentile or diplomacy 
		check to decide. 

		\begin{tabular}{r | c | l}
			\textsc{Boons}
			\hline
			1\%-25\% & DC <10 & He treats the party with indifference 
					or even as interupting intruders. Offers
					no important information about himself or
					the Red Wizards. \\
			26\%-50\% & DC 20 & He might tell the party about the Red
					Wizards as well as his own story of exile.
			


	\subsection{Groups and Factions}

		\subsubsection{The Iron Band}

		\subsubsection{Red Wizards}
	
		\subsubsection{Knights of Iomedae}

		\subsubsection{Knights of the Relic}

		\subsubsection{Order of Gozreh}

		\subsubsection{Lords of the Solid Hand}

		\subsubsection{The Keepers}

