\section{Places}

	\subsection{Grindstone Island}

		\subsubsection{Antioc}

		\subsubsection{Portland}

		\subsubsection{Hoath}
	
		\subsubsection{Northrun}
	
		\subsubsection{Algrem}

	\subsection{Ryujin}

		\subsubsection{Okashu}

		\subsubsection{Narahashi}

		\subsubsection{Aohiro}
	
		\subsubsection{Sakihiro}
	
		\subsubsection{Fukuhashi}

		\subsubsection{Hamakoku}

		\subsubsection{Iwoyama}

		\subsubsection{Oshu}

		\subsubsection{Toyama}

	\subsection{Wolf Island}

		\subsubsection{Edgehaven}

		\subsubsection{Hallowthicket}

		\subsubsection{Soluck}

		\subsubsection{Ilwarg}

		\subsubsection{Karmyrk}

		\subsubsection{Sokin}

	\subsection{Haunya}

		\subsubsection{Xicxil}
	
		\subsubsection{Takas}
	
		\subsubsection{N'Gulonga}

		A port city on the northern coast of Haunya, N'Gulonga has grown 
		in importance since the Northern Fires started.  With its proximity
		to Ko' Rau, the city has become a popular destination for adventurers
		on expeditions into the Burning North.  The port teems with all
		manner of travelers, merchants and adventurers, some heading into 
		the northern continent, others carrying goods to the Temple of 
		Iomedae.  Even though the Knights of the Relic rule over the city,
		trade on the black market continues to grow.  In recent years, the 
		unsavory trade of undead, devils and demons developed into a major 
		business.  

			\paragraph{NPCs}
				
			
			\paragraph{Shops}

			\paragraph{Encounters}
	
		\subsubsection{Tueha}

		\subsubsection{Totzal}

		\subsubsection{Yaiji}

		\subsubsection{Aztath}

		A small farming village at the edge of the great plains; this small 
		settlement is a frequent stop for merchant trains traveling between 
		Xicxil and N'Gulonga.  Due to its location, Aztath offers several 
		places for travelers to rest, resupply and repair equipment.  

			\paragraph{NPCs}
			
				\begin{itemize}
					\item \textsc{Cassandra}: A middle aged elf that runs 
							errands for the local tavern and inn.
							A self taught bard and archivist, she
							is able to point the party to most of
							the local goings on.  Keeps her precious
							records in the storeroom under the
							general store. 
					\item \textsc{Talas}: The young owner of the local
							general store, General Goods, acts as a 
							go between for clients and the thieves 
							guild.  Not a malicious individual,
							usually offers his services to people he
							knows and trusts.  Locals go to him whenever 
							they need specialty goods and respect him
							for being able to get almost anything.  
				\end{itemize}
			\paragraph{Shops}

				\begin{itemize}
					\item \textsc{Lyon's Gate}
					\item \textsc{S}
					\item \textsc{General Goods}
					\item \textsc{Blacksmith}
					\item \textsc{Tanner}
				\end{itemize}

			\paragraph{Encounters}
				\begin{itemize}
					\item Merchants traveling between N'Gulonga
						and Xicxil.
				\end{itemize}
				
		\subsubsection{Mattu}

		\subsubsection{Kingali}

	\subsection{Ko' Rau}

		\subsubsection{Temple of Iomedae}

		\subsubsection{Iron Citadel}

		\subsubsection{Teroia}

	\subsection{Southern Continent}

		\subsubsection{Irondale}

		\subsubsection{Land's End}

		\subsubsection{Highacre}
	
		\subsubsection{Darldour}

		\subsubsection{Tonsheim}

		\subsubsection{Osstrom}

		\subsubsection{Fagervik}

	\subsection{Sunken Cities}

		\subsubsection{Atlas}

		\subsubsection{Aquarius}
	
	\subsection{Notable Landmarks}

		\subsubsection{The Bluffs}
		
		\subsubsection{The Grand Library}

		\subsubsection{The Deeps}

		\subsubsection{Shifting Sands}
		
		In the middle of the Great Plains of Haunya, sleeps one of the
		worlds largest deserts. At least a weeks travel from end to end,
		few people who venture into the desert unprepared reach their 
		destination.  Resourceful nomads, roaming djinn and a few other
		tribes call the Sands home.  Most of the tribes know how difficult
		travel through the desert can be and treat all they meet with 
		unending hospitality, though others will defend their ancient 
		homeland to the death.  A perpetual sandstorm whirls around the
		center of the desert, guarding sunken city, Ubar or Iram of the 
		Pillars.  The legendary City of Brass, home to the djinn and
		efreeti, contains wonders and artifacts few have laid eyes upon
		in the past century.  

		\paragraph{Encounters}
			\begin{itemize}
				\item Groups of Djinn
				\item Groups of Div
				\item Other travelers
				\item Oasis 
				\item Nomads
				\item Desert giants
			\end{itemize}
		
		\paragraph{Ubar, The City of Brass}
