\section{Introduction}

Welcome to The Scorched Land campaign setting.  The following chapters will lay 
out the most important aspects of this world, however the DM is encouraged to 
alter the setting to fit their groups play style and goals.  Hopefully this document
will be helpful to beginner and veteran DMs alike.  In the following pages, I will 
attempt to cover all of back-story, party motivations, possible quests and important
NPCs that the party could encounter on their adventure.  Due to the size of the 
map and openness of the storyline, the DM will have the opportunity to fill in 
many of the blanks.

\section{Background}

A vast ocean encompasses most of the world, while autonomous city-states rule over
what land there is.  The city-state of Antioc, the Empire of Ryujin and the Dwarven
stronghold of Irondale rule most of the world around them.  Few places around the 
world fall outside their spheres of influence, due to location or to affiliations 
with other groups.

The city-state of Antioc sits on the smallest island in the area, Grindstone Island,
however due to its central location, the city has become rich and powerful.  Antioc
controls most of the trade routes, and serves as a convenient stop for ships 
traveling to other ports.  Archbishop-General Augustus XVII rules over Antioc and 
its colonies, as both the head of the Order of Iomedae and the Antiocan military,
Augustus holds supreme rule.  Antioc controls the city of N'Gulonga, which serves 
as a stop for ships bound for the Temple of Iomedae to the far north.  The leaders 
of Grindstone Island brokered a deal with the Jade Lady, Empress of Ryujin, allowing
for trade between the two nations.  With this agreement Antioc gained influence 
over trade routes between all the other nations.

The Empire of Ryujin lies to the east of Grindstone Island; Ryujin maintains a
constant state of isolationism, interacting with the other states only when
necessary.  The walled port of Okashu remains the only city where foreigners may
enter the country, and to travel outside its walls requires express permission 
from the Jade Lady.  As with all things people do not understand, the people
from the Empire are shrouded in lore and superstition: fighters that can disappear 
into nothingness, warriors that can scare off the most fiendish of beasts and
men that can kill with only a touch.  Very few outsiders are allowed into the 
country and even fewer have seen the Imperial City.  To the north and south of 
Okashu sits Narahashi and Aohiro, respectively.  From these fortressed cities the 
Empire keeps a close watch over all traffic in and out of Okashu.  Ships accused
of smuggling contraband to Okashu are never seen again.  

To the north-west of Grindstone sits Wolf Island, home of the Elvan city of 
Edgehaven. The island has long been coveted for its large old growth forests and 
rich soil.  However the Elvan tribunal know as The Masked Ones and their enforcers
the Order of Gozreh, forbid the taking of natural resources for profit.  Due to
its stance on harvesting natural resources tension continues between Edgehaven and 
Antioc, who would like to use the rich resources of Wolf Island to further expand
their wealth and influence.  Apart from the distrust between the two city-states
Edgehaven keeps a low profile, partly due to its focus on maintaining the Dark 
Woods, an old growth forest covering most of the island.

Haunya, the largest island, sits just to the west of Wolf Island.  Once home to
an ancient civilization, small tribes and ports controlled by brigands and out--
laws litter the island.  The largest cities, Xicxil and N'Gulonga, are located on
the southern and northern coasts, respectively.  N'Gulonga, a smaller port city,
acts as a vital life line into Ko' Rau, supplying the Temple of Iomedae with anything
the Knights require.  Xicxil, built on the ruins of a ancient city, has become
to the more unsavory characters.  Pirates, thieves and outlaws find a home and
protection from outside persecution.  Home to the thieves guild, the city functions
with relative peace, due to the strict code of conduct enforced by the guild.

To the north of the ocean exists Ko' Rau, the Scorched Land, once a prosperous and 
fertile land, now charred, cursed and abandoned by all but the most foolhardy.  Now
home to devils, demons and all manner of foul beasts, the continent spews forth 
a never ending army of horrors.  The only known settlement is the Temple of Iomedae,
home to the Knights of Iomedae, men and women that have dedicated their life to 
the eradication of the demonic forces.  Once a year on the Fall Equinox, Ko' Rau 
bursts into a hellish blaze, and the frequency of demonic encounters increases.

\section{Backstory}

For the past couple decades the Dark Continent of Ko' Rau, has birthed the most
disturbing horrors the world has ever seen.  Every year the army of hell-spawn
grows in size and territory.  At first the holy knights from Antioc were enough
to contain the spread, but now demons and other unholy blights have appeared in 
greats plains of Haunya and hiding in the Dark Woods of Wolf Island.  Fearing 
whats to come in the next couple years, Archbishop-General Augustus XVII has 
beseeched the other nations to send anyone they can to be apart of a coalition 
tasked with finding the reason for and stopping the yearly firestorm in the North.
Since the plea for help went out, people from all over the world have travelled 
to Antioc to take lend their strength in order to put an end to the phenomenon.

The adventuring party may have many origins, however they should eventually 
come to Antioc and become authorized as official participants in the campaign.
As members of the coalition, the party gains some boons.

	\begin{itemize}
		\item \textsc{Bronze Token}: Allows the party to stay at any
			barracks controlled by the Knights of the Relic.
		\item 2 \textsc{Potion of Cure Light Wounds}
	\end{itemize}

Party contains a member of the Knights of Antioc, the group may also purchase
or borrow adventuring gear for the Knights' quartermaster.  

