\section{People and Factions}
	
	\subsection{Important NPCs}

		\subsubsection{Augustus XVII}
			In the world of Antioc the might of the church and military are 
			placed into the hands one man, the Archbishop--General.  As the 
			current ruler of Antioc, Augustus XVII holds absolute power over
			the affairs of the nation.  Selected by a meeting of the leaders
			of the Knights of the Relic and Knights of Iomedae upon the death 
			of the previous Archbishop, Augustus was chosen to lead the nation
			after being decorated for his services as the commander of the Iron
			Citadel.  Being no stranger to the horrors birthed in Ko' Rau,  
			the new Archbishop--General has decided to throw the full might of 
			Antioc against the evil continent.  After three years with no 
			marked improvement, the Archbishop--General has made a plea for 
			help to all the surrounding nations.

		\subsubsection{The Masked Ones}
			
		\subsubsection{King Faerlag}

		\subsubsection{The Jade Lady}

		\subsubsection{Braga Blackthorn, Last King of Ko' Rau}
			Braga Blackthorn was the last king in a long line of dwarven rulers
			in the north.  During the time of his rule, the world witnessed the 
			fall of the greatest dwarven civilization to the first fires to 
			consume the northern country.  When he was a young dwarf, Braga become 
			the next King in the North when his father, Draga fell in battle 
			against the Red Wizards.  At the height of the war, the dwarves found 
			themselves in dire straights, with most of the their country overrun
			and without a way to fight against the Wizards' powerful circle magic.
			Braga brought together his best craftsmen and scholars to construct 
			five powerful artifacts that would render circle magic useless.  He 
			succeeded and sent one of each of these artifacts to the other capital
			cities around the world creating a circle magic suppression field.  
			Without the potency of their accursed magics, the residents of Ko' Rau
			were able to push the Red Wizards back to their last stronghold, The 
			Iron Tower.  Soon after the war ended, and Braga was considered the
			hero of his people.  Several years later, on the day of the surrender
			the capital city of Ko' Rau was consumed by unholy flames as the 
			first Fires of Dis ritual was performed.  In the blast, Braga perished,
			leaving behind only the holy amulet around his neck.  
			
			\textsc{Amulet of Braga}
			
			\begin{tabular}{| c | c | c |}
				\hline
				Neck & Strong Abjuration & Artifact \\
				\hline
			\end{tabular}
			
			The Amulet of Braga appears as a simple gold chain with the symbol of
			Torag as the pendent.  When a person first puts on the Amulet, their 
			soul is transported to the Grand Feasting Hall in old Ko' Rau.  At 
			the head of the table sits Braga, usually enjoying a fine meal.  As
			long as the wearer of the necklace is not evil or a Red Wizard, Braga
			is always cordial to his guest.  Even when his guest is not to his 
			liking, he is at least polite as his station dictates.  He is 
			particularly fond of craftsmen and mages.  The introductory 
			conversation takes 10 min, during which the wearers body sits still
			in a trance, if they are disturbed the trance ends.  After wearing 
			the amulet once, any wearer is aware of the amulets powers and how  to
			trigger them.  
			
			\begin{itemize}
				\item Wearer gains a passive +4 to crafting checks.  The wearer 
				is a smith of any kind, this bonus increases to +8.  
				\item The wearer gains fire resistance 20.
				\item Once a day, the wearer can spend 10 min to commune with Braga
				as per the \textit{commune} spell (CL 8).  
			\end{itemize}

	\subsection{Minor NPCs}

		\subsubsection{Andor, The Man in Red}

		Once a Red Wizard, Andor has been banished from the Iron Tower
		for speaking out against the yearly rituals and now lives atop
		a mountain on Haunya.  The local goblin tribe have adopted his
		Iron Band tattoo as their new crest and revere him as a wise 
		and powerful man.  Since the goblins live close to a mountain
		pass used frequently by the Thieves Guild as a smuggling route,
		they now raid carrivans, hoping to catch a group transporting
		some of the relics necessary for the Fires of Dis ritual, which
		is often referred to as 'Braga's Curse'.  He can grant the party 
		information or even a boon depending on how much he likes the 
		party.  A percentile or diplomacy check to decide.  

		\textsc{Boons}

		\begin{tabularx}{\textwidth}{| X | X | X |}
			\hline
			1\%-50\% & DC 15 & He treats the party with indifference 
						or even as interupting intruders. \\
 					& & Offers no important information about 
						himself or the Red Wizards. \\
			\hline
			51\%-75\% & DC 25 & He might tell the party about the Red
						Wizards as well as his own story \\ 
					& & 	of exile. \\
			\hline	
			76\%-100\% & DC 35 & Tells the party of the Fires of Dis 
						ritual and gives the party a letter of \\
					& &	introduction to help them find people 
						involved with the ritual. \\ 		
			\hline
		\end{tabularx}

		\subsubsection{Faust}

	\subsection{Groups and Factions}

		\subsubsection{The Red Wizards}

		\subsubsection{The Iron Band}
			\paragraph{The House of Sorrow}
			\paragraph{The House of Greed}
			\paragraph{The House of Whispers}
			\paragraph{The Grand Tower}

		\subsubsection{Knights of Iomedae}

		\subsubsection{Knights of the Relic}

		\subsubsection{Order of Gozreh}

		\subsubsection{Lords of the Solid Hand}

		\subsubsection{The Keepers}
		
		\subsubsection{Clan Lochlann}
			Crafters wonderous items

		\subsubsection{Clan Sinclair}
			Sorcerers, dragon and abberation bloodlines

		\subsubsection{Clan BlackWood}
			Arms and armor. pragmatic.

		\subsubsection{Clan Mulloy}
			Merchants.

